--- 
title: "My post-graduate study work"
author: "Karine Villeneuve"
affiliation: "University of Quebec in Montrealm(UQAM)"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo

---

# Introduction {#intro}

Welcome to my bookdown, a place where I keep step-by-step guides and general informations about my project. 

## About me 

My name is Karine Villeneuve and I am a post-graduate student working at the [lazar microbial ecology lab]() at the Univeristy of Quebec in Montreal. 


My research focuses on microbial communities that live in aquifers. More specifically I am interested in changes happening at the community level according to the seasons and in the migration of microorganism in the subsurface, from recharge to discharge area. 


I began my research in September 2019 after obtaining my bachelor's degree in environmental studies at the University of Sherbrooke. 


This led me on an unpexpected journey from Montreal to Texas. 





You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
